---
title: "Mediterranean Swordfish"
author: "Laurence Kell"
date: "21/07/2014"
output: word_document
---

Dropbox/swo-med/analysis/tex

```{r, echo=FALSE}
library(knitr)

opts_chunk$set(comment=NA, 
               fig.width =5.5, 
               fig.height=6,
               fig.path  ="../tex/",
               warning=FALSE, 
               message=FALSE, 
               error  =FALSE, 
               echo   =FALSE, 
               eval   =TRUE,
               cache  =TRUE)
```

```{r, echo=FALSE}
library(FLCore)
library(FLBRP)
library(ggplotFL)
library(mixdist)
library(ALKr)
library(FLsz)
library(FLXSA)
library(FLash)
library(mixdist)


theme_set(theme_bw(base_size=10))

## Functions
vonB=function(params,data){
  res=params["linf"]%*%(1.0-exp((-params["k"])%*%(data%-%params["t0"])))
  dimnames(res)=dimnames(data)
  res}

## Data and parameters
dirMy ="/home/laurie/Desktop/Dropbox/swo-med/analysis"
dirDat=paste(dirMy,"/Data",  sep="")
dirInp=paste(dirMy,"/Inputs",sep="")

par=FLPar(linf=238.59,k=0.185,t0=-1.404,a=8.90493e-7,b=3.554738,l50=142)

cas=read.csv(paste(dirInp,"casSWOM8513_v1.csv",sep="/"))

names(cas)=c("stock","year","flag","fleet","gear","sea","len","len5","n")
cas       =transform(cas, len    =len+0.5,
                     lustrum=(year%/%5)*5,
                     yr     =year-(year%/%5)*5,
                     wt     =par["a"]*(len^par["b"])/1000)

pi    =ageIt(cas$len,cas$n,par,timing=0.5,plusGroup=10)
grwPar=mixparam(pi    =pi[,2]/sum(pi[,2]),
                mu    =c(vonB(par,FLQuant(0:10+.5,dimnames=list(ages=0:10)))),
                sigma =rep(0.05,11))
grwPar$sigma<-grwPar$sigma*grwPar$mu

constr<-mixconstr(conmu ="MFX", 
                  fixmu=c(rep(FALSE,5),rep(TRUE,6)), 
                  #consigma ="CCV")
                  consigma ="SFX", 
                  fixsigma=c(rep(FALSE,3),rep(TRUE,8)))

```{r,echo=FALSE,cache=TRUE}     
#par(mfrow=c(6,5))
#par(mar=c(1,1,1,1))

lfs=dlply(cas,.(year), 
      function(x,constr,grwPar){
            
        dat=ddply(x,.(len), with, data.frame(freq=sum(n)))
        dat$len[dat$len==max(dat$len)]=Inf  
            
        res=mix(dat,grwPar,"norm",constr=constr,emsteps=3,print.level=0,steptol=1e-3)
        
        #plot(res)
        
        res},
        constr=constr,grwPar=grwPar)
save(lfs,constr,grwPar,file=paste(dirDat,"/lfs.RData",sep=""))

## catch, length and weight-at-age matrices
lcaa=ldply(as.list(lfs), 
      function(lf){
        
          lenFn=function(lf){
            dat=lf$mixdata
            apply(sweep(fitted(lf)$joint[-dim(dat)[1],],1,dat[-dim(dat)[1],"len"],"*"),2,sum)/
            apply(fitted(lf)$joint[-dim(dat)[1],],2,sum)}
          
          data.frame(age   =0:10,
                     length=lenFn(lf),
                     freq  =apply(fitted(lf)[[2]],2,sum))
        })
save(lcaa,file=paste(dirDat,"/mixdist.RData",sep=""))

names(lcaa)   =c("year","age","len","n")
names(lcaa)[4]="data"
caa           =as.FLQuant(lcaa[,-3])

names(lcaa)[3]="data"
laa           =as.FLQuant(lcaa[,-4])
waa           =par["a"]*laa^par["b"]
save(caa,laa,waa,par,file=paste(dirDat,"/caa.RData",sep=""))
```

```{rcas2caa,echo=FALSE, figure.width=12,figure.height=8}     
lfs.df=ldply(lfs, function(lf){

  fn =function(pi,mu,sigma,x) pi*dnorm(x,mu,sigma)
  fn2=function(x,lf,binwidth) {
    lp =lf$parameters
    pop=sum(lf$mixdata[,2])*binwidth
    res=mdply(lp,fn,x=x)*pop
      
    return(res)}
  
  modes<-fn2(lf$mixdata[,1],lf,binwidth=1)

  data.frame(expand.grid(age     =as.numeric(dimnames(lf$parameters)[[1]])-1,
                         length=lf$mixdata$len),
                         freq  =melt(modes[,-(1:3)])[,2])})

ggplot(cas) +
  geom_histogram(aes(len,weight=n/5),
                 col="lightgreen", fill="white",border="green", binwidth=5) +
  geom_line(aes(length,freq,group=age),
                 col="red",data=lfs.df)+
  geom_line(aes(length,V1),
                 col="darkgreen",
                 data=ddply(lfs.df,.(length,year), with, sum(freq))) +
  facet_wrap(~year)+xlab("Length (cm)")+ylab("Numbers")+
  theme_bw(base_size=8)+
  scale_x_continuous(limits=c(50,250))
```
**Figure 1.** Length Frequencies with age modes (red) and total distributions (green) from the statistical estimation overlayed.


```{rcaa,fig.height=4}
slice  =ddply(cas,.(year), function(x) ageIt(x$len,x$n,par,timing=0.5,plusGroup=10))
names(slice)[3]="data"
slice=as.FLQuant(slice[,-4])

ggplot(as.data.frame(slice))+
  geom_point(aes(year,age,size=data))+
  theme(legend.position="none")+
  scale_size_area(max_size=8,  guide="none") +
  xlab("Year")+ylab("Age")+
  scale_y_continuous(breaks=seq(0,8,2))
```
**Figure 2.** Deterministic numbers-at-age from age slicing procedure.


```{rcaa2,fig.height=4}
ggplot(as.data.frame(caa))+
  geom_point(aes(year,age,size=data))+
  theme(legend.position="none")+
  scale_size_area(max_size=8,  guide="none") +
  xlab("Year")+ylab("Age")+
  scale_y_continuous(breaks=seq(0,8,2))
```
**Figure 3.** Statistical estimates of numbers-at-age  from the mixture distribution analysis.


```{r}
dat=transform(as.data.frame(FLQuants(Statistical  =caa,
                                     Deterministic=slice),drop=T),
              lustrum=(year%/%5)*5,
              yr     =year-(year%/%5)*5,
              Method =qname,
              data   =data/1000)[,-4]

ggplot(dat)+
  geom_bar(aes(age,weight=data,fill=Method), 
           alpha=1, position="dodge",binwidth=1,col="grey50")+
  facet_grid(yr~lustrum)+
  xlab("Age")+ylab("Numbers (1000s)")+
  scale_fill_manual(values=c("blue","red"))+
  theme(legend.position="bottom")
```
**Figure 4.** A comparison of catch numbers-at-age from the statistical and deterministic ageing procedures.


```{rsraa,fig.height=4}
res=slice%/%apply(slice,2,sum)
res=res%-%apply(res,1,mean)
res=res%/%apply(res,1,sd)

ggplot(as.data.frame(res))+
  geom_point(aes(year,age,size=data,
                 col=ifelse(data<0,"negative","positive")))+
  theme(legend.position="none")+
  scale_size(range=c(0,8),  guide="none") +
  xlab("Year")+ylab("Age")+
  scale_y_continuous(breaks=seq(0,8,2))+
  theme_bw()+
  scale_colour_manual(values=c("red","black"),guide="none")
```
**Figure 5.** Standardised residuals of the proportion of numbers-at-age from the deterministic age slicing procedure (red negative and black positive residuals).


```{raa2,fig.height=4}
res=caa%/%apply(caa,2,sum)
res=res%-%apply(res,1,mean)
res=res%/%apply(res,1,sd)

ggplot(as.data.frame(res))+
  geom_point(aes(year,age,size=data,
                 col=ifelse(data<0,"negative","positive")))+
  theme(legend.position="none")+
  scale_size(range=c(0,8),  guide="none") +
  xlab("Year")+ylab("Age")+
  scale_y_continuous(breaks=seq(0,8,2))+
  theme_bw()+
  scale_colour_manual(values=c("red","black"),guide="none")
```
**Figure 6.** Standardised residuals for the proportion of numbers-at-age from the statistical mixture distribution analysis (red negative and black positive residuals).


```{r}
swom=readFLStock(paste(dirInp,"swo.idx",sep="/"),no.discards=TRUE)
u   =readFLIndices(paste(dirInp,"swo.tun",sep="/"))

xsaCtrl <-FLXSA.control(shk.n  = TRUE, shk.yrs  = 5,  rage  = 1, 
                        shk.f  = TRUE, shk.ages = 5, fse    = 0.3,      
                        qage   = 6,
                        window = 100,  tsrange = 20,   tspower = 3, 
                        vpa    = TRUE)

xsaCtrl2<-FLXSA.control(shk.n  =TRUE,  shk.yrs =5,  rage   =1,     
                        shk.f  =TRUE,  shk.ages=1,  fse    =0.5, min.nse=0.3,     
                        qage   =6,
                        window =100,   tsrange =20, tspower=3, 
                        vpa    =TRUE)

m.spwn(      swom)[]  =0.5
harvest.spwn(swom)[]  =0.5
range(swom)[c("minfbar","maxfbar")]=c(2,4)

load(paste(dirDat,"/caa.RData",sep=""))
catch.n(swom)   =caa/1000
landings.n(swom)=caa/1000
catch        =landings(swom)

catch.wt(   swom)=waa
landings.wt(swom)=waa
discards.wt(swom)=waa
stock.wt(   swom)=waa

catch(swom)=catch

swom=setPlusGroup(swom,5)
stock.wt(swom)=catch.wt(swom)
```

```{rcatch,fig.height=4}
load(paste(dirDat,"swo2009PG10.RData",sep="/"))

biomass=cbind(ddply(cas,.(year), with, data.frame("CAS-Growth Curve"=sum(wt*n))),
              "2014 Task 1" =c(landings(swom)),
              "2014 CAA-WAA"=c(apply(waa*caa,2,sum))/1000)
b2009=as.data.frame(FLQuants("2010"  =catch(swo2009PG10)/1000,
                             "2010 CAA-WAA"=computeCatch(swo2009PG10)/1000))

ggplot(melt(biomass,id="year"))+
  geom_line(aes(year,value,group=variable,col=variable))+
  geom_line(aes(year,data,group=qname,col=qname),data=b2009)+
  scale_y_continuous(limits=c(0,25000))+
  theme(legend.position="bottom")
```
**Figure 7.** Comparison of total catch biomass derived from different procedures.

```{r}
mean(landings(swom)/computeCatch(swom))
```

```{rcas2,fig.height=6}
ggplot(ddply(cas,.(lustrum), transform, n=n/sum(n)))+
  geom_histogram(aes(x=len,y=..density..,weight=n),binwidth=5,
                 fill="steelblue",col="grey25")+
  facet_grid(lustrum~.)+
  scale_y_continuous(breaks=c(0.01))+
  theme_bw()+
  xlab("Length (cm)")+ylab("Density")
```
**Figure 8.** Catch-at-size by lustrum (5 year block).


```{rpw}
powh=function(len,n){
  
  fn=function(len,n){
    require(plyr)
    
    res=ddply(data.frame(n=n,len=len), .(len), function(x) sum(x$n))
    res=res[order(res$len),]
    
    csum =rev(cumsum(rev(res$V1)))
    clsum=rev(cumsum(rev(res$len*res$V1)))
    mn   =clsum/csum
    
    data.frame(mn=mn,diff=mn-res$len,len=res$len,n=res$V1)}
  
  linf=function(x) -coefficients(x)[1]/coefficients(x)[2]
  zk  =function(x) (-1-coefficients(x)[2])/coefficients(x)[2]
 
  dat=fn(len,n)
  
  res=lm(diff~len,data=dat)
  
  params=c("linf"=linf(res),"zk"=zk(  res))
  names(params)=c("linf","zk")
  
  return(list(params=params,
              data  =dat))}

pw=ddply(subset(cas), .(year), 
            function(cas) powh(cas$len,cas$n)$data)
      
pw=transform(pw, lustrum=(year%/%5)*5,
                 yr    =year-(year%/%5)*5,
                 weight=ifelse(len>=100&len<=200,1,0))

ggplot(pw)+
  geom_line(aes(len,diff,colour=factor(yr),group=year))+
  scale_x_continuous(limits=c(0,300)) +
  facet_wrap(~lustrum,ncol=2)+
  theme(legend.position="none")+
  xlab("Length (cm)")+
  ylab("Difference between Length and Mean Size")+
  geom_smooth(aes(len,diff,weight=weight),
              method="lm",col="red",size=1.25,alpha=.1)
```
**Figure 9.**  Powell-Wheatherall plots


```{rpwz,fig.height=3,length=8}
ggplot(transform(ddply(subset(cas,len>=100&len<=200), .(year), 
            function(cas) powh(cas$len,cas$n)$params),
         z=zk*par["k"]))+
  geom_point(aes(year,z))+
  geom_line(aes(year,z))+
  geom_smooth(aes(year,z),se=FALSE,span=.75,size=1.5)+theme_bw()
```
**Figure 10.** Estimates of Z derived from the Powell-Wetherall plots; showing the estimates from each year (black line with points) and a smoother (blue continuous line).


```{r}
ccFn=function(freq,age){
    freq=freq/sum(freq)
    lm  =lm(log(freq)~age)
    hat =exp(predict(lm))
    sel =(freq/hat)/max(freq/hat)
    data.frame(age=age,obs=freq,hat=hat,sel=sel)}

ca=ddply(cas, .(lustrum), 
          function(x,par,plusGroup,timing)
                 ageIt(x$len,x$n,par,timing,plusGroup), 
                      par=par, plusGroup=10, timing=0.5)

cc=ddply(subset(ca,age<10),.(lustrum),function(obj) ccFn(obj$freq,obj$age))

ggplot(cc)+
  geom_point(aes(age,log(obs)))+
  stat_smooth(aes(age,log(obs),weight=ifelse(age%in%2:8,1,0)),
              method="lm",se=FALSE)+
  facet_wrap(~lustrum,ncol=2)+theme_bw()+
  ylab(expression(log(P[a])))+xlab("Age")
```
**Figure 11.** Catch curves by lustrum from statisical age estimates.


```{r}
ggplot(cc, aes(age,sel))+
  geom_point()+
  geom_line(data=subset(cc,age<=5))+
  geom_line(data=subset(cc,age>=5),linetype=3)+
  facet_wrap(~lustrum,ncol=2)+theme_bw()+
  ylab("Selectivity-at-Age")+xlab("Age")

save(cc,file=paste(dirDat,"cc.RData",sep="/"))
```
**Figure 12.** Estimated selectivity by lustrum.


##Selectivity by gear
```{r,fig.height=5}
ca=ddply(cas, .(gear), 
          function(x,par,plusGroup,timing)
                 ageIt(x$len,x$n,par,timing,plusGroup), 
                      par=par, plusGroup=10, timing=0.5)

cc=ddply(subset(ca,age<10),.(gear),function(obj) ccFn(obj$freq,obj$age))

ggplot(cc,aes(age,sel))+
  geom_point()+
  geom_line(data=subset(cc,age<=5))+
  geom_line(data=subset(cc,age>=5),linetype=3)+
  facet_wrap(~gear,ncol=3)+
  ylab("Selectivity-at-Age")+xlab("Age")+
  scale_y_continuous(breaks=c(0,.5,1))+
  theme_bw()
```
**Figure 13.** Catch curves by gear based on age estimates


##Selectivity by gear and lustrum
```{r,fig.height=5}
ca=ddply(subset(cas,year>=2006), .(gear,lustrum), 
          function(x,par,plusGroup,timing)
                 ageIt(x$len,x$n,par,timing,plusGroup), 
                      par=par, plusGroup=10, timing=0.5)

cc=ddply(subset(ca,age<10),.(gear,lustrum),function(obj) ccFn(obj$freq,obj$age))

ggplot(cc,aes(age,sel,col=factor(lustrum),group=lustrum))+
  geom_point()+
  geom_line(data=subset(cc,age<=5))+
  geom_line(data=subset(cc,age>=5),linetype=3)+
 facet_wrap(~gear,ncol=3)+
  theme(legend.position="bottom")+
  ylab("Selectivity-at-Age")+xlab("Age")+
  scale_y_continuous(breaks=c(0,.5,1))
```
**Figure 14.** Catch curves by gear and lustrum based on statistical age estimates.


## XSA Continuity Run

```{r,fig.height=5,}
xsa=FLXSA(swom,u,xsaCtrl)
swom=swom+xsa

units(stock.n( swom))="Thousands"
units(stock.wt(swom))="Tonnes"

#plot(swom)+
#  facet_wrap(~qname,ncol=2,scale="free")

save(swom,u,xsa,xsaCtrl,
     file=paste(dirDat,"xsa.RData",sep="/"))
```

```{r}
dgs=mdply(data.frame(u=names(u)), function(u,xsa)
  model.frame(FLQuants(obs     =xsa@index[[u]]%/%xsa@q.hat[[u]],
                       hat     =xsa@stock.n[dimnames(index(xsa)[[u]])$age,
                                            dimnames(index(xsa)[[u]])$year],
                       residual=index.res(xsa)[[u]]),drop=T),xsa=xsa)
dgs=ddply(dgs,.(u,age),diags:::diagsFn)
```

```{ruhat}
ggplot(dgs,aes(hat,residual))+
  geom_point()+
  geom_hline(aes(yintercept=0))+
  facet_grid(u~age,scale="free_x")
```
**Figure 15.** XSA diagnostics from continuity run; residuals against fitted value.

```{rursd}
ggplot(dgs,aes(year,residual))+
  geom_point()+
  geom_errorbar(aes(year,ymin=0,ymax=residual))+
  geom_smooth(span=1,se=F)+
  facet_grid(u~age)
```
**Figure 16.** XSA diagnostics from continuity run; residuals against year.

```{rursd2,fig.height=4}
ggplot(subset(dgs,age==2),aes(hat,obs))+
  geom_abline(aes(a=0,b=1))+
  geom_point()+
  geom_smooth(method="lm")+
  facet_wrap(~u,ncol=3)+
  coord_cartesian(ylim=c(0,1000))
```
**Figure 17.** XSA diagnostics from continuity run; Calibration regression plots for age 2 (outlier for Scilian gillnet removed).

```{rursd3,fig.height=4}
ggplot(subset(dgs,age==3),aes(hat,obs))+
  geom_abline(aes(a=0,b=1))+
  geom_point()+
  geom_smooth(method="lm")+
  facet_wrap(~u,scale="free",ncol=3)+
  coord_cartesian(ylim=c(0,400))
```
**Figure 18.** XSA diagnostics from continuity run; Calibration regression plots for age 3 (outlier for Scilian gillnet removed).

```{rursd4,fig.height=4}
ggplot(subset(dgs,age==4),aes(hat,obs))+
  geom_abline(aes(a=0,b=1))+
  geom_point()+
  geom_smooth(method="lm")+
  coord_cartesian(ylim=c(0,200))+
  facet_wrap(~u,scale="free",ncol=3)
```
**Figure 19.** XSA diagnostics from continuity run; Calibration regression plots for age 4 (outlier for Scilian gillnet removed).


```{ruar,fig.height=6}
ggplot(dgs,aes(residual,residualLag))+
  geom_hline(aes(yintercept=0))+
  geom_point()+
  geom_smooth(method="lm",se=F)+
  facet_grid(age~u,scale="free")
```
**Figure 20.** XSA diagnostics from continuity run; AR plots of lagged residuals

```{rqq,fig.height=4}
ggplot(dgs)                                           +
  geom_point( aes(qqx,qqy))                            +
  stat_smooth(aes(qqx,qqHat),method="lm",se=T,fill="blue", alpha=0.1)         +
  facet_grid(age~u)                                    +
  theme(legend.position="bottom")  
```
**Figure 21.** XSA diagnostics from continuity run; QQ plots to check for normality


```{rWts}
ggplot(subset(xsa@diagnostics,age>0))+
  geom_point(aes(as.numeric(yrcls),nhat,size=0),shape=1,alpha=0)+
   geom_point(aes(as.numeric(yrcls),nhat,fill=factor(age),size=w),shape=21,
              data=subset(xsa@diagnostics,age>0&w>0))+
  geom_vline(aes(xintercept=2008.5))+
  facet_grid(source~age)+
  theme(legend.position="none")
```
**Figure 22.** XSA diagnostics from continuity run; weights for terminal year Ns for each CPUE observation and shrinkage

```{rsingleU,fig.height=6.5}
stks=FLStocks(mlply(data.frame(u=names(u)), function(u,swom,idx,ctrl){
 swom+FLXSA(swom,idx[[u]],ctrl)
  },swom=swom,idx=u,ctrl=xsaCtrl2))
stks[["Candidate"]]=swom

plot(stks)+
  theme(legend.position="bottom")
```
**Figure 23.** XSA time series estimates by CPUE series.

```{rRetro}
plot(FLStocks(mlply(data.frame(year=2009:2013), function(year,swom,u,ctrl){
  stk=window(swom,end=year)  
  stk+FLXSA(stk,u,ctrl)
  },swom=swom,u=u,ctrl=xsaCtrl)))+
  theme(legend.position="none")
```
**Figure 24.** Retrospective XSA time series estimates.

## Alternative Run

```{r,fig.height=5,}
xsa=FLXSA(swom,u,xsaCtrl2)
swom=swom+xsa
candidate=swom

units(stock.n( swom))="Thousands"
units(stock.wt(swom))="Tonnes"

#plot(swom)+
#  facet_wrap(~qname,ncol=2,scale="free")

save(swom,xsa,xsaCtrl2,
     file=paste(dirDat,"xsaAlt.RData",sep="/"))
```

```{r}
dgs=mdply(data.frame(u=index.name(xsa)), function(u,xsa)
  model.frame(FLQuants(obs     =xsa@index[[u]]%/%xsa@q.hat[[u]],
                       hat     =xsa@stock.n[dimnames(index(xsa)[[u]])$age,
                                            dimnames(index(xsa)[[u]])$year],
                       residual=index.res(xsa)[[u]]),drop=T),xsa=xsa)
dgs=ddply(dgs,.(u,age),diags:::diagsFn)
```

```{ruhat-alt}
ggplot(dgs,aes(hat,residual))+
  geom_hline(aes(yintercept=0))+
  geom_point()+
  facet_grid(u~age,scale="free_x")
```
**Figure 25.** XSA diagnostics from alternative run; residuals against fitted value.

```{rursd-alt}
ggplot(dgs,aes(year,residual))+
  geom_point()+
  geom_errorbar(aes(year,ymin=0,ymax=residual))+
  geom_smooth(span=1,se=F)+
  facet_grid(u~age)
```
**Figure 26.** XSA diagnostics from  from alternative run; residuals against year.

```{rursd2-alt,fig.height=4}
ggplot(subset(dgs,age==2),aes(hat,obs))+
  geom_abline(aes(a=0,b=1))+
  geom_point()+
  geom_smooth(method="lm")+
  facet_wrap(~u,scale="free",ncol=3)+
  coord_cartesian(ylim=c(0,1000))
```
**Figure 27.** XSA diagnostics from  from alternative run; Calibration regression plots for age 2.

```{rursd3-alt,fig.height=4}
ggplot(subset(dgs,age==3),aes(hat,obs))+
  geom_abline(aes(a=0,b=1))+
  geom_point()+
  geom_smooth(method="lm")+
  facet_wrap(~u,scale="free",ncol=3)+
  coord_cartesian(ylim=c(0,400))
```
**Figure 28.** XSA diagnostics from alternative run; Calibration regression plots for age 3.

```{rursd4-alt,fig.height=4}
ggplot(subset(dgs,age==4),aes(hat,obs))+
  geom_abline(aes(a=0,b=1))+
  geom_point()+
  geom_smooth(method="lm")+
  coord_cartesian(ylim=c(0,200))+
  facet_wrap(~u,scale="free",ncol=3)
```
**Figure 29.** XSA diagnostics from alternative run; Calibration regression plots for age 4.


```{ruar-alt,fig.height=6}
ggplot(dgs,aes(residual,residualLag))+
  geom_hline(aes(yintercept=0))+
  geom_point()+
  geom_smooth(method="lm",se=F)+
  facet_grid(age~u,scale="free")
```
**Figure 30.** XSA diagnostics alternative run; AR plots of lagged residuals

```{rqq-alt,fig.height=4}
ggplot(dgs)                                           +
  geom_point( aes(qqx,qqy))                            +
  stat_smooth(aes(qqx,qqHat),method="lm",se=T,fill="blue", alpha=0.1)         +
  facet_grid(age~u)                                    +
  theme(legend.position="bottom")  
```
**Figure 31.** XSA diagnostics alternative run; QQ plots to check for normality

```{rWts-alt,figure.height=4}
ggplot(subset(xsa@diagnostics,age>0))+
  geom_point(aes(as.numeric(yrcls),nhat,size=0),shape=1,alpha=0)+
   geom_point(aes(as.numeric(yrcls),nhat,fill=factor(age),size=w),shape=21,
              data=subset(xsa@diagnostics,age>0&w>0))+
  geom_vline(aes(xintercept=2008.5))+
  facet_grid(source~age)+
  theme(legend.position="none")
```
**Figure 32.** XSA diagnostics alternative run; weights for terminal year Ns for each CPUE observation and shrinkage

```{rsingleU-alt,fig.height=6.5}
stks=FLStocks(mlply(data.frame(u=names(u)), function(u,swom,idx,ctrl){
 swom+FLXSA(swom,idx[[u]],ctrl)
  },swom=swom,idx=u,ctrl=xsaCtrl2))
stks[["Candidate"]]=swom

plot(stks)+
  theme(legend.position="bottom")
```
**Figure 33.** XSA time series estimates by CPUE series.

```{rRetro-alt}
plot(FLStocks(mlply(data.frame(year=2009:2013), function(year,swom,u,ctrl){
  stk=window(swom,end=year)  
  stk+FLXSA(stk,u,ctrl)
  },swom=swom,u=u[c(1,6)],ctrl=xsaCtrl2)))+
  theme(legend.position="none")
```
**Figure 34.** Retrospective XSA time series estimates.

## Stock Status
```{rU16}
plot(swom)+
  theme(legend.position="none")
```
**Figure 35.** XSA alternative run.

## Stock Status
```{rsr}
sr=as.FLSR(swom,model="bevholt")
sr=fmle(sr,control=list(trace=0),fixed=list(b=10))
plot(sr)
```
**Figure 36.** Stock Recruitment Relationship

```{r}
discards.n(swom)[]=0
swom=setPlusGroup(swom,10)

landings.wt(swom)[]=apply(waa[,ac(2011:2013)],1,mean)
discards.wt(swom)=landings.wt(swom)
stock.wt(   swom)=landings.wt(swom)

brp=FLBRP(swom,sr=sr)

brp=brp(brp)

save(swom,brp,sr,file=paste(dirDat,"brp.RData",sep="/"))

plot(brp)+theme(legend.position="bottom")
```
**Figure 37a.** Equilibrium Analysis with reference points.

```{r}
plot(brp,obs=TRUE,refpts=FALSE)+theme(legend.position="bottom")
```
**Figure 37b.** Equilibrium Analysis with observations.


```{r}
library(kobe)
kobePhase(kobe(brp,swom),xlim=c(0,2))+
  geom_path(aes(stock,harvest,col=year))+
  theme(legend.position="none")

save(brp,swom,file=paste(dirDat,"/shiny.RData",sep=""))
```
**Figure 38.** Kobe Phase Plot.

```{rsel}
load(paste(dirDat,"pel.RData",sep="/"))

pel=setPlusGroup(FLQuant(c(0,pel[,"sel"]),
                         dimnames=list(age=0:9)),10)
pel[ac(6:10)]=pel["5"]
sel=landings.sel(brp)

load(paste(dirDat,"brp.RData",sep="/"))
ggplot(as.data.frame(FLQuants("Current"    =landings.sel(brp)/max(landings.sel(brp)),
                              "Mesopelagic"=pel)))+
  geom_line(aes(age,data,col=qname,group=qname))+
  theme(legend.position="bottom")
```
**Figure 39.** Current and mesopelagic selection patterns.

```{r}
set.seed(9789)
srDev=exp(FLQuant(sample(c(residuals(sr)[,ac(1985:2010)]),26*100,T),
            ,dimnames=list(year=2014:2025,iter=1:100)))

f=FLQuant(mean(c(fbar(swom)[,ac(2011:2013)])),dimnames=list(year=2014:2025))
    
swom.=fwdWindow(swom,end=2025,brp)
swoms=fwd(swom.,
          FLQuants(f=f,f=f*0.8),
          sr=brp,
          sr.residuals=srDev)
    
refPtSQ=computeRefpts(brp)[1:6,1:5]

names(swoms)=c("F Status Quo","F Reduction")
plot(swoms)+
  facet_wrap(~qname,ncol=1,scale="free")+
  theme(legend.position="bottom")
```
**Figure 40.** Projections for current selection pattern.

```{r}
selMult=0.5

landings.sel(brp)=sel*selMult+pel*(1-selMult)
refPtMP=computeRefpts(brp)[1:6,1:5]

swom.=fwdWindow(swom,end=2025,brp)
swoms=fwd(swom.,
          FLQuants(f=f,f=f*0.8),
          sr=brp,
          sr.residuals=srDev)
    
names(swoms)=c("F Status Quo","F Reduction")
plot(swoms)+
    facet_wrap(~qname,ncol=1,scale="free")+
    theme(legend.position="bottom")
```
**Figure 41.** Projections for 50:50 current:mesopelagic selection pattern.


Tables
=====================================

Table 1a. XSA Control options from continuity run.
```{r}
xsaCtrl
```

Table 1b. XSA Control options from alternative run.
```{r}
xsaCtrl2
```

Table 2a. Reference Points
```{r}
refPtSQ[1:6,1:5]
```

Table 2b. Reference Points with 50% Mesopelagic selection pattern.
```{r}
refPtMP[1:6,1:5]
```

Table 3. Stock information
```{r}
candidate
```

Table 4a. XSA diagnostics from continuity run.
```{r}
diagnostics(xsa)
```

Table 4b. XSA diagnostics from alternative run.
```{r}
diagnostics(xsa)
```
